\documentclass[a4paper,10pt,draft,twocolumn]{article}

% Packages.
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[style=ieee,backend=biber]{biblatex}
%\usepackage{booktabs}
%\usepackage{caption}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{listings}
%\usepackage{mathtools}
%\usepackage{physics}
\usepackage{siunitx}
%\usepackage{subcaption}
%\usepackage{subfiles}
%\usepackage{tabularx}
%\usepackage{varioref}
\usepackage{xcolor}

% Packages settings.
\addbibresource{bibliography.bib}
%\captionsetup{tableposition=top,figureposition=bottom,font=footnotesize,format=hang,subrefformat=parens}
\hypersetup{hidelinks}
%\DeclareGraphicsExtensions{.pdf,.jpg,.png}
\graphicspath{{./figures/}}
\sisetup{group-digits=integer,separate-uncertainty,per-mode=fraction}

% Customization.
\definecolor{Blue}{rgb}{0.2,0.2,0.9}
\definecolor{Green}{rgb}{0,0.6,0}
\definecolor{Gray}{rgb}{0.5,0.5,0.5}
\definecolor{Purple}{rgb}{0.58,0,0.82}
\definecolor{background}{rgb}{0.98,0.98,0.95}
\lstdefinestyle{mystyle}{
  backgroundcolor=\color{background},
  commentstyle=\color{Green},
  keywordstyle=\color{Blue},
  numberstyle=\tiny\color{Gray},
  stringstyle=\color{Purple},
  basicstyle=\ttfamily\footnotesize,
  breakatwhitespace=false,
  breaklines=true,
  captionpos=b,
  keepspaces=true,
  numbers=left,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=2
}
\lstset{style=mystyle}

\newcommand{\cpp}{C++}
\newcommand{\dd}{\mathop{}\!\mathrm{d}}
\newcommand{\PTOA}{P_\mathrm{TOA}}

\raggedbottom

% Document.
\begin{document}
\title{Study Nuclear Winter with a radiative-convective climate model} % MC choose title.
\author{Marco Casari}
\date{\today}
\maketitle

\begin{abstract}
  % MC abstract.
\end{abstract}

% MC add if needed, probably not.
%\tableofcontents
%\newpage

\section{Introduction}
% MC the aim of this project is presented.
% MC the physical background is presented.
Planet Earth's climate dynamics can be studied with models of varying complexity depending on the subject of the study. Radiative-convective models (RCMs) provide an intermediate complexity approach to the simulation of climate, evaluating the atmospheric temperature profile in a vertical column where temperature is averaged over all latitudes and longitudes.

The present work intends to study the atmospheric temeprature profile averaged on the Northern Hemisphere in presence of conditions 

%\section{Materials}

\section{Methods}
% MC explain the atmosphere model: vertical column where each layer present quantities averaged over the global atmosphere.
The RCM developed for the present work approximates the atmosphere as a vertical column divided in a given number of layers.
% MC put the number of layers.

% MC explain the subdivision between the radiative part and the convective part.
% MC distinguish in appropriate subsections the treatment of shortwave and longwave radiations and radiation scattering vs absorption.

% MC describe conventions used in this work.
\subsection{Hypotheses and conventions}
\label{sec:Hypotheses and conventions}
To simplify some calculations for radiative fluxes, the definition of wavenumber $\nu = \frac{1}{\lambda}$ is used in this work, where $\lambda$ is the wavelenght.

Specific gas constant is used in thermodynamical relations, which is defined as the gas constant divided by the gas molar mass. In this work the symbol $R$ is used for the specific gas constant.

Some assumptions are made on state and composition of Earth's atmosphere. 
% MC do I need to use the International Standard Atmosphere? It is not a wise choice since its temperature profile is already fixed. But I can take it as reference for other parametrizations.
Gravitational acceleration $g$ is constant (cfr. Table~\ref{tab:constants} for values). Air parcels are supposed to be in hydrostatic equilibrium,
\begin{equation}
  \label{eq:hydrostatic_equilibrium}
  \dd P = - \rho g \dd z
\end{equation}
with each component obeying the ideal gas law
\begin{equation}
  \label{eq:ideal_gas_law}
  P = \rho R T
\end{equation}
where $\rho = \frac{m}{V}$ is the volumetric mass density of the air parcel.

% MC put constants in a table, not in the appendix since it is part of the data needed to understand the main text. This table has headers: symbol, value, unit of measure, notes (e.g. long name of the constant).

Solar radiation is considered orthogonal to the plane which represents Earth's surface in the RCM. Constant solar irradiance $S_0$ is used in calculations.
% MC introduce the approximation where visible and UV radiation from the Sun and IR radiation from the Earth are uncorrelated in Earth's atmosphere (i.e. their spectral wavebands do not overlap), hence the fluxes of the two types of radiation are treated independently.

\subsection{Longwave radiation}
% MC TTAPS-I: absorption of longwave radiation.
At wavelengths $\lambda \geq \qty{4}{\micro\metre}$, solar radiation has lower intensities than radiation emitted by Earth's surface and atmosphere at the same wavelengths. Moreover, it presents negligible scattering in atmosphere with respect to absorption. For these reasons longwave radiation is considered to be emitted only by Earth's surface and atmosphere.\cite[468]{ramanathan}

% MC continue with formulae.

\subsection{Shortwave radiation}
% MC TTAPS-I: absorption and scattering of shortwave radiation.
At wavelengths $\lambda < \qty{4}{\micro\metre}$, solar radiation has much greater intensity than radiation emitted from Earth's surface and atmosphere. Both scattering and absorption by gases, aerosols and clouds of atmosphere dissipates solar radiation.\cite[469]{ramanathan}

Specific intensity of solar radiation can be expressed by a differential equation whose resolution is complex even applying approximations and numerical methods.\cite[469]{ramanathan}

A lower complexity parametrisation is adopted instead, where the atmosphere is divided in a given number of layers and radiation is absorbed, scattered and reflected between each layes. Multiple reflections can occur from each layer but only one is considered in this model because successive reflections from amospheric layers have negligible intensities compared to the first one.\cite[470]{ramanathan}

% MC continue with formulae.

\subsection{Numerical treatment}
% MC convert the problem and the physical formulae into the numerical algorithms and functions to solve it.
% MC show and describe formulae.
% MC explain that the integration scheme is explicit since the evaulation is made at the same time step, not at the next time step. Probably it is better if the evaluation of fluxed is made implicitly to guarantee numerical stability.

Euler's method is used to solve the Ordinary Differential Equation (ODE) for the time-dependant temperature function.\cite[472]{ramanathan} A solution for each atmospheric layer is evaluated, hence the resulting values are triplets of temperature, altitude (i.e. proxy for the atmospheric layer) and time (i.e. simulation time). Further information on storage and plotting of data are presented in Section~\ref{sec:Plotting}.

% MC how many spectral bands have I chosen? Maybe list them in a table in the appendix with notes for each band to explain why I have chosen that band (e.g. to excite the vibro-rotational levels of some gases).
Spectral bands are identified by two arrays: one listing the lower bound of each band, the other containing the width of each band. This choice simplify the use of functions for numerical integration. Values related to spectral bands are stored as integers.

\section{Results}
% MC explain briefly how to read a skew-T plot.
% MC show and comment obtained plots.

\subsection{Stability analysis}
% MC the equilibrium temperature profile is insensitive of the initial guess temperature profile for the time-stepping (i.e. Euler) approach.\cite[473]{ramanathan}

\section{Discussion}
% MC sum up what I did and the results compared with article TTAPS-I.
% MC if there is enough time, use the results and the comparison with TTAPS-I as model validation then gain some insights on the same results using the contemporary nuclear arsenal and compare with the modern version of TTAPS (i.e. Turco 2008, compare what is possible since it is made with a GCM).

%\section{Conclusion} % MC instead create a "Discussion and conclusion" section.

\newpage
\appendix

\section{Source code}
In this section the \cpp\ code used to obtain the results presented in this work is shown and commented.
% MC show the whole source code, splitted in sections.

% MC some thoughts about the development of the code.
First, the parametrization of the vertical coordinate is chosen among three alternatives: altitude $z$ in \unit{\metre}, atmospheric pressure $P$ in \unit{\pascal}, coordinate $\sigma = \frac{P - \PTOA}{P_S - \PTOA}$ adimensional, with $\PTOA$ pressure at the top of the modelised atmosphere and $P_S$ pressure at the surface. One parametrisation can be written in term of another through a monotonic function (e.g. pressure decreases with altitude, cfr. Appendix~\ref{sec:Relation between pressure and altitude}). For the initial development the altitude $z$ is chosen as vertical coordinate because it is more intuitive, moreover plots in TTAPS-I are expressed in terms of both $z$ and $P$.

Second, the atmospheric layers are configured. In TTAPS-I 20 layers are used (cfr. \cite[396]{NuclearWinterPhysics}) and they are numbered from the top of the atmosphere down as it is common in RCMs. The vertical coordinate refers to the center of each layer, with the excpetion of the last layer which is in direct contact with the surface and needs to be treated separately. % MC "Temperatures are calculated at the midpoints of the layers, and fluxes are computed at the layer boundaries."\cite[449]{Catling}
Therefore two arrays are needed: one for the point and one with the corresponding layer thicknesses. Values are then assigned as double precision numbers. The value corresponding to the top of the atmosphere is set in a proper variable and a uniform distribution of layer thicknesses is assumed for ease.

% MC radiative fluxes are computed for each atmospheric layer.
To reduce the computation load of radiative fluxes, only some spectral intervals are considered and they are specific to each atmospheric layer, since the available absorbing gases and aerosols differ among layers. First absorbers for each layer are stored in an array, then the spectral bandwitdhs needed for each layer are evaluated. Spectral bandwidths are expressed in terms of wavenumbers with unit \unit{\per\centi\metre} to manage integer values or double precision values close to unity. For each chemical species the absorption intervals are identified by their width and central wavenumber, the former are obtained from the latter and using the exponential wide band model (cfr. \cite[360]{Modest}). These two values are stored in separate arrays.

\subsection{Classes}
% MC show and comment the source code for the used classes.

\section{Supplementary information}

\subsection{Plotting}
\label{sec:Plotting}
Software Gnuplot is used to generate plots shown in this work. Output values from the simulation are stored in a DAT file with the following structure, line spacing between data blocks is important:
\begin{verbatim}
t[0]       P[0]       T[0][0]
...        ...        ...
t[0]       P[N_P - 1] T[0][N_P - 1]

t[1]       P[0]       T[1][0]
...        ...        ...
t[1]       P[N_P - 1] T[1][N_P - 1]

...

t[N_t - 1] P[0]       T[N_t - 1][0]
...        ...        ...
t[N_t - 1] P[N_P - 1] T[N_t - 1][N_P - 1]
\end{verbatim}
Value \verb|N_t| is not known a priori since it is the number of temporal steps needed to reach convergence, instead \verb|N_P| is the chosen number of atmospheric layers.

\section{Mathematical derivations}
In this appendix mathematical derivations of some ancillary results and formulae used in the main text are explicitly shown.

\subsection{Relation between pressure and altitude}
\label{sec:Relation between pressure and altitude}
A general result regarding planetary atmosphere is that atmospheric pressure decreases with increasing altitude. Theoretical relations which approximate this behaviour can be obtained. Hypotheses considered in Section~\ref{sec:Hypotheses and conventions} are valid.

If density is assumed constant, equation~\eqref{eq:hydrostatic_equilibrium} can be solved easily resulting in a linear dependence of pressure $P$ on altitude $z$, % MC normalize the way I refere to sections and equations.
\begin{equation}
  \label{eq:pressure_constant_density}
  P(z) = P_0 - \rho g (z - z_0)
  \quad ,
\end{equation}
where $(z_0, P_0)$ is a reference point inside the atmosphere.

If density is not constant its expression is given by the ideal gas law (cfr. equation~\eqref{eq:ideal_gas_law}) and, assuming constant temperature $T$, equation~\eqref{eq:hydrostatic_equilibrium} results in:
\begin{equation}
  \label{eq:pressure_constant_temperature}
  \begin{split}
    & \dd P = - \frac{P g}{R T} \dd z \iff \\
    \iff & \frac{\dd P}{P} = - \frac{g}{R T} \dd z \impliedby \\
    \impliedby & \ln(P') \bigg|_{P_0}^{P(z)} = - \frac{g}{R T} z' \bigg|_{z_0}^{z} \iff \\
    \iff & P(z) = P_0 \exp{\bigg( - \frac{g}{R T} (z - z_0) \bigg)}
    \quad .
  \end{split}
\end{equation}
This relation is not meaningful, since the aim of the work is to derive the non-constant temperature profile of the atmosphere. However, it can be used inside atmospheric layers where the temperature is considered constant (e.g. stratosphere).

A better approximation assumes non-constant density and constant lapse rate $\Gamma$, hence temperature depends linearly on altitude,
\begin{equation}
  \label{eq:constant_lapse_rate}
  \Gamma = - \frac{\dd T}{\dd z} \impliedby T(z) = T_0 - \Gamma (z - z_0)
  \quad ,
\end{equation}
with $T_0$ temperature corresponding to reference altitude $z_0$. Using these assumptions and the density rewritten through the ideal gas law \eqref{eq:ideal_gas_law}, equation~\eqref{eq:hydrostatic_equilibrium} becomes
\begin{equation}
  \label{eq:pressure_constant_lapse_rate}
  \begin{split}
    & \dd P = - \frac{P g}{R T} \bigg( - \frac{\dd T}{\Gamma} \bigg) \iff \\
    \iff & \frac{\dd P}{P} = \frac{g}{R \Gamma} \frac{\dd T}{T} \impliedby \\
    \impliedby & \ln(P') \bigg|_{P_0}^{P(z)} = \frac{g}{R \Gamma} \ln(T') \bigg|_{T_0}^{T(z)} \iff \\
    \iff & P(z) = P_0 \bigg( \frac{T_0 - \Gamma (z - z_0)}{T_0} \bigg)^\frac{g}{R \Gamma}
  \end{split}
\end{equation}
% MC choose a better format for splitted equations.

Equation \eqref{eq:pressure_constant_lapse_rate} can be used also with a piecewise constant lapse rate in altitude intervals where it is not null. Otherwise, in altitude intervals where lapse rate is null, equation \eqref{eq:pressure_constant_temperature} is valid with appropriate boundary conditions to ensure continuity between layers.

\subsection{Radiometric quantities}
\label{sec:Radiometric quantities}
Refer to \cite{CIE} for more details on quantities reviewed in this section.

Consider electromagnetic radiation emitted by a point source. The total emitted power is called \emph{radiant flux}, with unit \unit{\watt}. The density of radiant flux with respect to a solid angle in the direction of emission is called \emph{radiant intensity}, expressed in \unit{\watt\per\steradian}. When radiation interacts with a surface, i.e. it gets absorbed, transmitted or reflected, its radiant intensity distributed over the surface is measured through \emph{radiance} in \unit{\watt\per\square\metre\per\steradian}. If the area on which the radiation is incident is expressed through the solid angle it subtends, the integral of radiance over this solid angle is called \emph{irradiance}, expressed in \unit{\watt\per\square\metre}. Note that the coordinate system where the solid angles of radiant intensity and irradiance are defined may not be the same.

% MC if needed make a consideration for the case where there is no source and only the radiation incident on a surface is considered.

All previous quantities can be expressed as densities with respect to the wavelength or the wavenumber and the adjective \emph{spectral} is prefixed to their names. Their units are divided by the respective spectral quantity (e.g. spectral radiance with wavenumber in \unit{\per\centi\metre} has units \unit{\watt\per\metre\squared\centi\metre\per\steradian}).

Spectral radiance of a blackbody is given by Planck's law
\begin{equation}
  \label{eq:blackbody_radiance}
  B_\nu (\nu, T) = 2 h c^2 \nu^3 \frac{1}{e^\frac{h c \nu}{k_B T} - 1}
  \quad ,
\end{equation}
where $\nu$ is the wavenumber in unit \unit{\per\centi\metre} (cfr. notation in section~\ref{sec:Hypotheses and conventions}), $T$ in unit \unit{\kelvin} is the temperature of the emitting body and the other quantities are constants (cfr. table~\ref{tab:constants}).

If the radiance is isotropic, i.e. it has not dependence on the direction of the radiation, the corresponding irradiance is proportional. For instance, if the radiation is absorbed by a hemispheric surface approximated by a blackbody, the spectral irradiance of the surface is
\begin{equation}
  \label{eq:blackbody_irradiance_hemisphere}
  \begin{split}
    & \int B_\nu (\nu, T) \dd \phi \sin(\theta) \dd \theta \cos(\theta) = \\
    & = B_\nu (\nu, T) \int_0^{2\pi} \dd \phi \int_0^\frac{\pi}{2} \sin(\theta) \cos(\theta) \dd \theta = \\
    & = 2 \pi B_\nu (\nu, T) \int_0^1 \sin(\theta) \dd(\sin(\theta)) = \\
    & = 2 \pi B_\nu (\nu, T) \frac{1}{2} = \pi B_\nu (\nu, T)
  \end{split}
  \quad ,
\end{equation}
where spherical coordinates are used to describe the surface and the term $\cos(\theta)$ considers the component of radiation along the normal of the infinitesimal solid angle.

\newpage
\printbibliography[heading=bibintoc]
\end{document}
